Optimal (Multiway) Spatial Joins

### 2024-06-03 msj.tex
yufei

\extraspacing \underline{\em Proof of Statement (3).} We first prove that $\dcross_H(\bm{t}) \neq \emptyset$ for any $\bm{t} \in \J(R_1',...,R_{k-2}')$. Set $r' = \gbot(\bm{t})$, and let $r$ be the full rectangle of $r'$. Define $h$ as the lowest segment crossing $r$ (note that $h$ definitely exists because otherwise $r$ has no trimmed rectangle, contradicting the definition of $r'$). We will show that $h \in \dcross_H(\bm{t})$ and hence $\dcross_H(\bm{t}) \ne \emptyset$. For this purpose, we should explain why $h$ crosses both $B_{\bm{t}}$ and $r'$. However, $h$ crossing $r$ implies $h$ crossing $r'$, as we already know from the above proof of statement (2). It remains to show that $h$ crosses $B_\bm{t}$.

>>>>

\extraspacing \underline{\em Proof of Statement (3).} We start by proving that $\dcross_H(\bm{t}) \neq \emptyset$ for any $\bm{t} \in \J(R_1',...,R_{k-2}')$. Set $r' = \gbot(\bm{t})$, and let $r$ be the full rectangle of $r'$. Define $h$ as the lowest segment crossing $r$ (note that $h$ definitely exists because otherwise $r$ has no trimmed rectangle, contradicting the definition of $r'$). We will show that $h \in \dcross_H(\bm{t})$ and hence $\dcross_H(\bm{t}) \ne \emptyset$. For this purpose, we should explain why $h$ crosses both $B_{\bm{t}}$ and $r'$. However, $h$ crossing $r$ implies $h$ crossing $r'$, as we already know from the above proof of statement (2). It remains to show that $h$ crosses $B_\bm{t}$.
